### 2025-03-19 player-evaluation.qmd
20250319 - changes in player situation

For players who have played in the NFL, past performance becomes more relevant because, presumably, the prior situation is more similar (than was their situation in college) to their current situation.
Nevertheless, lots of things change from game to game and season to season: injuries, coaches, coaching strategies, teammates, etc.
So just because a player performed well or poorly in a given game or season does not necessarily mean that they will perform similarly in subsequent games/seasons.
Nevertheless, historical performance is one of the best indicators we have.

@@

>>>>

For players who have played in the NFL, past performance becomes more relevant because, presumably, the prior situation is more similar (than was their situation in college) to their current situation.
Nevertheless, as described below, lots of things change from game to game and season to season, and such changes are important to monitor because they can render prior situations less relevant to the player's current situation.
Thus, it is important not to rely just on a player's historical performance from last season.
Nevertheless, historical performance is one of the best indicators we have.

@@

#### Changes in Situational Factors {#sec-evalChanges}

Lots of things change from game to game and season to season: injuries, coaches, coaching strategies, teammates, etc.
Just because a player performed well or poorly in a given game or season does not necessarily mean that they will perform similarly in subsequent games/seasons.
Thus, it is crucial to consider the player's current situation—and what has changed since the prior game or season.
Consider what has changed in terms of [situational factors](#sec-evalSituation):

- Is the player on a new team?
- Do they have a new head coach or coordinator?
- How will the team's offensive scheme change?
- Does the team have a better offensive line?
- Does the team have better receiving targets?
- Will the player's position change on the depth chart?
- Will there be more competition for targets?

There is often greater uncertainty in selecting a player who has changed teams or whose situation has greatly changed, but such risk can be highly rewarded when the player's new team or situation is better suited to the player.
If a player underachieved on a given team, they may perform better for another team.
